Inventor Disambiguation Report

### 2022-05-31 examples/templates/index.qmd
update

    - rawinventor.parquet

@@

disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.parquet'] }
```

@@

### rawinventor.parquet

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="reference")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="reference")
```

>>>>

    - rawinventor.tsv

@@

disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.tsv'] }
```

@@

### rawinventor.tsv

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.tsv"], load_israeli_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.tsv"], load_patentsview_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.tsv"], load_israeli_inventors_benchmark()), by="reference")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.tsv"], load_patentsview_inventors_benchmark()), by="reference")
```
